Distances

### 2020-04-09 03_distances.Rmd
Add error handling and python script for data processing

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(reticulate)
use_condaenv("ox", conda = "~/opt/anaconda3/condabin/conda")
```

@@

import numpy as np
import pandas as pd
import time
import multiprocessing as mp
```

@@

```{python graph}
graph = ox.graph_from_place('New York, New York, USA', network_type='drive')
graph_proj = ox.project_graph(graph)
```

@@

First, we bring the park points we sampled into a pandas data frame with
the park id as the index.
```{python park_points_py}
park_points = pd.DataFrame(r.park_points)
# TODO: run for all park points
park_ids = park_points.sample(5).id

@@

def parallelize_dataframe(df, func, n_cores=4):
  df_split = np.array_split(df, n_cores)
  pool = Pool(n_cores)
  df = pd.concat(pool.map(findnode, df_split))
  pool.close()
  pool.join()
  return df

@@

    # loop through points
    for point in these_points.itertuples():
      # get length between park and this edge point
      length = nx.shortest_path_length(graph_proj, source = bg.node, target=point.node,
        weight = 'length')

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(reticulate)
library(tidyverse)
library(sf)
library(leaflet)
use_condaenv("ox", conda = "~/opt/anaconda3/condabin/conda", required = TRUE)
```

@@

import numpy as np
import pandas as pd
import time
```

@@

```{python graph}
graph = ox.graph_from_place('New York, New York, USA', network_type='walk')
graph_proj = ox.project_graph(graph)
```

@@

First, we bring the park points we sampled into a pandas data frame with
the park id as the index.
```{python park_points_py}
park_points = pd.DataFrame(r.park_points)
# TODO: run for all park points
park_ids = park_points.sample(2).id

@@

@@

    # loop through points
    for point in these_points.itertuples():
      # get length between park and this edge point
      try:
        length = nx.shortest_path_length(graph_proj, source = bg.node, target=point.node,
          weight = 'length')
      except:
        length = float("inf")

@@

```{python write}
park_points.to_csv("data/park_points.csv")
blockgroups.to_csv("data/blockgroups.csv")
```
